Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/intro.tex
x

To evaluate whether Nail's design is effective at handling real-world data
formats, we implemented a prototype of Nail for C\@. Using our prototype, we
implemented succinct grammars for parts of an IP network stack, for DNS packets,
and for ZIP files, each in about a hundred lines of grammar. On top of these
grammars, we were able to build a DNS server in under 200 lines of C code, and
an {\tt unzip} utility in about 50 lines of C code, with performance comparable
to or exceeding existing implementations. This suggests both that Nail is
effective at handling complex real-world data formats, and that Nail makes it
easy for application developers to parse and generate external data
representations. Performance results show that the Nail-based DNS server
outperforms the widely used BIND DNS server, demonstrating that Nail-based
parsers and generators can achieve good performance.

>>>>

To evaluate whether Nail's design is effective at handling real-world data
formats, we implemented a prototype of Nail for C\@. Using our prototype, we
implemented grammars for parts of an IP network stack, for DNS packets,
and for ZIP files, each in about a hundred lines of grammar. On top of these
grammars, we were able to build a DNS server in under 200 lines of C code, and
an {\tt unzip} utility in about 50 lines of C code, with performance comparable
to or exceeding existing implementations. This suggests both that Nail is
effective at handling complex real-world data formats, and that Nail makes it
easy for application developers to parse and generate external data
representations. Performance results show that the Nail-based DNS server
outperforms the widely used BIND DNS server, demonstrating that Nail-based
parsers and generators can achieve good performance.
